Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-21 paper.qmd
Update with quollr new

```{r}
## Compute hexbin parameters
num_bins_x_scurve <- 6
num_bins_y_scurve <- 14
hex_size_scurve <- 0.13
buffer_x_scurve <- 0.338
buffer_y_scurve <- 0.292
x_start_scurve <- -0.113
y_start_scurve <- -0.098

>>>>

```{r}
## Compute hexbin parameters
num_bins_x_scurve <- 6
num_bins_y_scurve <- 10
hex_size_scurve <- 0.13
buffer_x_scurve <- 0.338
buffer_y_scurve <- 0.292
x_start_scurve <- -0.113
y_start_scurve <- -0.098
